{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-09-09 Notebook LaTEX/Momentum Accelerations/paper.tex
=w=, fixes and shit

            % \\& 
            % \begin{aligned}
            %     &= h(z) + 
            %         \langle \mathcal G_L(x), x^+ - z\rangle 
            %     - \frac{\mu}{2}\Vert z - x\Vert^2
            %     + \frac{L}{2}\Vert x - x^+\Vert^2
            % \end{aligned}
            % \\& 
            % \begin{aligned}
            %     &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
            %     - \frac{\mu}{2}\Vert z - x\Vert^2
            %     + \frac{L}{2}\Vert x - x^+\Vert^2
            % \end{aligned}
            % \\&
            % \begin{aligned}
            %     &= h(z) + 
            %     \underbrace{\langle L(x - x^+), x - z\rangle}_{
            %         = - \langle \mathcal G_L (x), z - x\rangle
            %     }
            %     - \frac{\mu}{2}\Vert z - x\Vert^2
            %     - \frac{L}{2}\Vert x - x^+\Vert^2
            % \end{aligned}

@@

        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + \partial g(x^+)$, it yields

@@

            \le h(z) + 

@@

@@

        Observe that we have 

@@

            \quad &

@@

            Since $a_t = \tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 

>>>>

@@

        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + v = L(x - x^+)$, so it yields

@@

            h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 

@@

            \underbrace{\langle L(x - x^+), x - z\rangle}_{
                = - \langle \mathcal G_L (x), z - x\rangle
            - \frac{L}{2}\Vert x - x^+\Vert^2

@@

        Observe that we have for all $u$: 

@@

            h(u) &\ge 

@@

            Since $a_t = L\tilde \eta_t$, and the Nesterov sequence exhibits $a_{t} \ge (t + 2)/2$, the convergence becomes $\mathcal O(T^{-2})$. 
